A Case Study in Preserving a High Energy Physics Application

### 2014-01-17 paper.tex
Give an introduction to the tau analysis.
A high-level, more abstract view of our concept of data analysis.  May need
more refinement.

\documentclass{acm_proc_article-sp}
\usepackage{url}
\begin{document}

@@

>>>>

\documentclass{acm_proc_article-sp}
\usepackage{url}
\usepackage{siunitx}
\begin{document}

@@

Within the ongoing investigation of the Higgs boson at the CMS
detector, part of the LHC at CERN, the Higgs production in association
with two top quarks allows to measure the Higgs coupling strength to
top quarks.  As the Higgs boson cannot be detected itself, it has to
be reconstructed from its decay products.  The analysis discussed in
this section focuses on the Higgs decaying to two tau leptons, which
are reconstructed from particle showers.

The CMS collaboration provides analysis end-users with a pre-processed
and reduced data format, AOD, containing information for events, i.e.,
proton-proton collisions with a signature of interest, in the form of
reconstructed particles.  This format is based on the RAW output of
the CMS detector readout electronics and reconstructed world-wide.
Both real and simulated data are available for examination.

As AOD data are too large to be iteratively processed repetitively in
an physics analysis workflow, it is normally reduced further in
structural complexity and content.  For the analysis under
investigation here, this is a two-step process.  First, the AOD data
are processed at the Notre Dame working group cluster to BEAN events,
containing only trivial data containers packed in vectors.  This step
is time and CPU intensive and contains data of \SI{11.6}{TB} to be
analyzed by the tau analysis.  The BEAN format and data is shared
within the analysis group looking at Higgs production in association
with top quarks, which is formed by groups from a few American and
European universities.

In the second step, which is the beginning of the actual tau analysis,
the data are reduced to variables relevant to the tau analysis, while
only events matching basic quality criteria are kept.  This results in
a dataset of \SI{43.3}{GB}.  Again, the Notre Dame CMS groups cluster
resources are used to perform this reduction and selection, with
highly customized software.

The final data analysis, investigated below, can be run as a single
process, and contains a stringent event selection to keep only high
quality candidate events for the underlying physical process (using
\SI{122}{MiB} of space).  Quantities from the selected events can be
both plotted and used in multivariate analysis to determine the level
of expected signal in real data.

% FWIW, units are TB, GB, not TiB, GiB!
